---
title: "Shiny with RMarkdown"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Our datasets came from the Los Angeles area, and we decided to look at a sample of 10,000 car crashes that occurred between 2010 and the present. Weather data was also joined to this to look at what sort of connection was present there (not that LA weather is much to deal with, but it could still be a factor).

```{r, include=FALSE}
library(tidyverse)
```

```{r, include=FALSE}


#install.packages("maps")
#install.packages("mapdata")
#install.packages("ggmap")
#install.packages("mapproj")
#install.packages("ggplot2")
#install.packages("plotly")

library(maps)
library(mapdata)
library(ggmap) #use to read map
library(mapproj) #map tools kits
library(ggplot2) #read the map data
library(tidyverse)
library(stringr)

register_google(key = "AIzaSyARb0Fsx8OYgRVToJK_2Abl4r1lO_1ACCY", write = TRUE)

```

```{r, include=FALSE}
collisions_subset_10000 <- read.csv("Collision 10000.csv")
#collisions_subset_10000 <- collisions[sample(nrow(collisions),10000),]

extract_numbers <- function(string){ 
  str_extract(string, "\\-*\\d+\\.*\\d*")
} 

collisions_subset_10000_renamed <- collisions_subset_10000 %>%
rename("Row original" = X,
       "Division of Records" = DR.Number,
       "Date Reported" = Date.Reported,
       "Date Occurred" = Date.Occurred,
       "Time Occurred" = Time.Occurred,
       "Area ID" = Area.ID,
       "Area Name" = Area.Name,
       "Reporting District" = Reporting.District,
       "Crime Code" = Crime.Code,
       "Crime Code Description" = Crime.Code.Description,
       "Modus Operandi Codes" = MO.Codes,
       "Victim Age" = Victim.Age,
       "Victim Sex" = Victim.Sex,
       "Victim Descent" = Victim.Descent,
       "Premise Code" = Premise.Code,
       "Premise Description" = Premise.Description,
       "Cross Street" = Cross.Street,
       "Zip Codes" = Zip.Codes,
       "Census Tracts" = Census.Tracts,
       "Precinct Boundaries" = Precinct.Boundaries,
       "LA Specific Plans" = LA.Specific.Plans,
       "Council Districts" = Council.Districts,
       "Neighborhood Councils" = Neighborhood.Councils..Certified.)%>%
  mutate(`Date Reported` = parse_date(str_sub(`Date Reported`, 0, 10)),
         `Date Occurred` = parse_date(str_sub(`Date Occurred`, 0, 10)),
         `Date Reported` = as.Date(`Date Reported`),
         `Date Occurred` = as.Date(`Date Occurred`))%>%
  separate(Location, c("Longitude","Latitude"), sep =',' )%>%
  mutate(Longitude = as.numeric(extract_numbers(Longitude)),
         Latitude = as.numeric(extract_numbers(Latitude))) %>%
  mutate(Longitude = as.character(extract_numbers(Longitude)),
         Latitude = as.character(extract_numbers(Latitude)),
         Longitude = as.numeric(Longitude),
         Latitude = as.numeric(Latitude)) 
  


# typeof(collisions_subset_10000_renamed$`Date Reported`)
# str(collisions_subset_10000_renamed)
# View(collisions_subset_10000_renamed)
#importing weather data 
#LAweather1 <- read_csv("~/Mscs 264 S19/Submit/MSCS_PROJECT_2019/LAweather1.csv")

#Code of the weather and tidy weather 1 and 2
LAweather1 <- read_csv("LAweather1.csv")
#View(LAweather1)
LAweather_US1CALA0030_1  <- LAweather1 %>%
  filter( STATION == "US1CALA0030")
#View(LAweather_US1CALA0030_1)

LAweather1.1 <- LAweather1 %>%
  select(DATE, PRCP)
#View(LAweather1.1)
LAweather1.1 <- LAweather_US1CALA0030_1 %>%
  select(DATE, PRCP) %>%
  mutate(date = as.Date(DATE))%>%
  rename("Date Occurred" = date)

#View(LAweather1.1)


#Renaming the dataset of the weather1.1 in order to make easier the merge with the collision dataset

final_weather_collision_1.1 <- merge(x = LAweather1.1,
                                 y= collisions_subset_10000_renamed, 
                                 by = "Date Occurred", all = TRUE)
#view(final_weather_collision_1.1)


#Reading weather 2 and mergin to final_weather_collision by PRCP
#LAweather2 <- read_csv("~/Mscs 264 S19/Submit/MSCS_PROJECT_2019/LAweather2.csv")
LAweather2 <- read_csv("LAweather2.csv")

LAweather_US1CALA0030_2  <- LAweather2 %>%
  filter( STATION == "US1CALA0030")
#View(LAweather_US1CALA0030_2)
  

LAweather2.1 <- LAweather_US1CALA0030_2 %>%
  select(PRCP)
#view(LAweather2.1)

LA_Collision_weather_complete <- merge(x = final_weather_collision_1.1, 
                                       y = LAweather2.1,
                                       by = "PRCP", all = TRUE)
#view(LA_Collision_weather_complete)


LA_Collision_complete_tidy<-LA_Collision_weather_complete[c(1,2,4:28)] 


#View(LA_Collision_complete_tidy)




  

#typeof(collisions_subset_10000_renamed$Longitude)

#str(collisions_subset_10000_renamed)
#str(collisions_subset_10000_renamed)
#view(collisions_subset_10000_renamed)
#write.csv(collisions_subset, "Collision 5000.csv")
#write.csv(collisions_subset_10000_renamed, "tidy_collisions.csv")

```

```{r, include=FALSE}
LA_map <- get_map(location = "los angeles, california", zoom = 11)
#ggmap(LA_map)
```

```{r, include=FALSE}
#heatmap 


#all crashes
mapsetall <- LA_Collision_complete_tidy %>%
  select(Longitude, Latitude) %>% 
  na.omit()


#morning crashes 
mapset1 <- LA_Collision_complete_tidy %>%
  select(Longitude, Latitude, `Time Occurred`) %>% 
  filter(`Time Occurred` < 900) %>%
  na.omit()


#evening crashes 
mapset2 <- LA_Collision_complete_tidy %>%
  select(Longitude, Latitude, `Time Occurred`) %>% 
  filter(`Time Occurred` > 1800) %>%
  na.omit()

#midday crashes 
mapset3 <- LA_Collision_complete_tidy %>%
  select(Longitude, Latitude, `Time Occurred`) %>% 
  filter(`Time Occurred` < 1500) %>%
  filter(`Time Occurred` > 900) %>%
  na.omit()

#crashes only while raining
mapsetrain <- LA_Collision_complete_tidy %>%
  select(`Area Name`, Longitude, Latitude, `PRCP`) %>% 
  filter(`PRCP` > 0) %>%
  na.omit()


allmap <- ggmap(LA_map) + geom_density_2d(aes(x = Longitude, y = Latitude), data = mapsetall) +
  stat_density2d(data = mapsetall, 
    aes(x = Longitude, y = Latitude, fill = ..level.., alpha = ..level..), size = 0.01, 
    bins = 16, geom = "polygon") + scale_fill_gradient(low = "green", high = "red", 
    guide = FALSE) + scale_alpha(range = c(0, 0.3), guide = FALSE)

morningmap <- ggmap(LA_map) + geom_density_2d(aes(x = Longitude, y = Latitude), data = mapset1) +
  stat_density2d(data = mapset1, 
    aes(x = Longitude, y = Latitude, fill = ..level.., alpha = ..level..), size = 0.01, 
    bins = 16, geom = "polygon") + scale_fill_gradient(low = "green", high = "red", 
    guide = FALSE) + scale_alpha(range = c(0, 0.3), guide = FALSE)


eveningmap <- ggmap(LA_map) + geom_density_2d(aes(x = Longitude, y = Latitude), data = mapset2) +
  stat_density2d(data = mapset2, 
    aes(x = Longitude, y = Latitude, fill = ..level.., alpha = ..level..), size = 0.01, 
    bins = 16, geom = "polygon") + scale_fill_gradient(low = "green", high = "red", 
    guide = FALSE) + scale_alpha(range = c(0, 0.3), guide = FALSE)


middaymap <- ggmap(LA_map) + geom_density_2d(aes(x = Longitude, y = Latitude), data = mapset3) +
  stat_density2d(data = mapset3, 
    aes(x = Longitude, y = Latitude, fill = ..level.., alpha = ..level..), size = 0.01, 
    bins = 16, geom = "polygon") + scale_fill_gradient(low = "green", high = "red", 
    guide = FALSE) + scale_alpha(range = c(0, 0.3), guide = FALSE)

rainmap <- ggmap(LA_map) + geom_density_2d(aes(x = Longitude, y = Latitude), data = mapsetrain) +
  stat_density2d(data = mapsetrain, 
    aes(x = Longitude, y = Latitude, fill = ..level.., alpha = ..level..), size = 0.01, 
    bins = 16, geom = "polygon") + scale_fill_gradient(low = "green", high = "red", 
    guide = FALSE) + scale_alpha(range = c(0, 0.3), guide = FALSE)



#allmap
#rainmap
#eveningmap

```

```{r, include = FALSE, warning=FALSE, echo=TRUE}
#importing weather data 
# LAweather1 <- read_csv("~/Mscs 264 S19/Submit/MSCS_PROJECT_2019/LAweather1.csv")
# View(LAweather1)
# LAweather1 %>% 
#   filter(STATION == "US1CALA0036")

#LAweather2 <- read_csv("~/Mscs 264 S19/Submit/MSCS_PROJECT_2019/LAweather2.csv")
#View(LAweather2)

LA_Collision_complete_tidy %>%
ggplot(aes(x =  `Time Occurred`, y = `Victim Age`, color = `Victim Sex` )) + 
  #geom_point() +
  geom_smooth( se = FALSE, na.rm = TRUE) +
  ylim(0, 100) %>%
  labs(y="Victim Age", 
       x="Time", 
       title="Victims age by time")



library(plotly)
ani_raw <-  sample_n(LA_Collision_complete_tidy, 5000)
renderPlot(
ani_raw %>%
  plot_ly(x = ~`Neighborhood Councils`, y = ~`Victim Age`, size = ~`Victim Age`, 
          text = ~`Victim Sex`, hoverinfo = "text") %>%
  layout(xaxis = list(type = "log"))%>%
  add_markers(color = ~`Victim Sex`, frame = ~`Time Occurred`, ids = ~`Victim Descent`) %>%
  animation_opts(1000, easing = "elastic", redraw = FALSE) %>%
  animation_button(x = 1, xanchor = "right", y = 0, yanchor = "bottom"
  ) %>%
  animation_slider(
    currentvalue = list(prefix = "Time Occurred", font = list(color="red"))
  ))
```


```{r, include=FALSE}


#shiny app - interactive graph with buttons and sliders up top 
  
#heatmap and stuff below 
```



How  crash location or behavior changes with the weather in LA

```{r, echo=FALSE, warning=FALSE}
inputPanel(
  checkboxInput("type_check", "Raining?", value = FALSE)
  
)
renderPlot({
     if (!input$type_check) 
        allmap
     else if (input$type_check)      
        rainmap
})
```

Looking at crashes in the morning versus evening rush 

```{r, echo=FALSE, warning=FALSE}
inputPanel(
  checkboxInput("type_check2", "Evening Rush?", value = FALSE)
  
)
renderPlot({
     if (!input$type_check2) 
        morningmap
     else if (input$type_check2)      
        eveningmap
})
```

Visualizing crashes in a particular LA neighborhood

```{r, echo=FALSE}
titlePanel("Area of Crashes")

inputPanel(
  selectInput("neighborhood", label = "Neighborhood",
    choices = c("Central" = "Central",
                "Hollywood" = "Hollywood",
                "North Hollywood" = "N Hollywood",
                "Rampart" = "Rampart", 
                "Olympic" = "Olympic", 
                "Southwest" = "Southwest",
                "Newton" = "Newton",
                "Southeast" = "Southeast",
                "Pacific" = "Pacific", 
                "Hollenbeck" = "Hollenbeck",
                "Foothill" = "Foothill"
                ))
  
)
renderPlot({
  
    LA_Collision_complete_tidy %>%
  select(`Area Name`, Longitude, Latitude) %>% 
  filter(`Area Name` == input$neighborhood) %>%
  na.omit() 
    ggmap(LA_map) + geom_density_2d(aes(x = Longitude, y = Latitude), data = LA_Collision_complete_tidy %>%
  select(`Area Name`, Longitude, Latitude) %>% 
  filter(`Area Name` == input$neighborhood) %>%
  na.omit()) +
  stat_density2d(data = LA_Collision_complete_tidy %>%
  select(`Area Name`, Longitude, Latitude) %>% 
  filter(`Area Name` == input$neighborhood) %>%
  na.omit(), 
    aes(x = Longitude, y = Latitude, fill = ..level.., alpha = ..level..), size = 0.01, 
    bins = 16, geom = "polygon") + scale_fill_gradient(low = "green", high = "red", 
    guide = FALSE) + scale_alpha(range = c(0, 0.3), guide = FALSE)
  
  
})
```



















